Decision analysis for Bergen

### 2017-02-02 code/BergenDecisions/BergenDamageData.Rmd
Minor changes to Rmd file

---
title: "Decision analysis for Bergen"
author: "Thordis L. Thorarinsdottir"
output:
    html_document:
    toc: TRUE
---

<hr></hr>
<br></br>

## Optimal timing of sea level rise adaptation measures in Bergen, Norway

@@

@@

Investigation of the effects of uncertainty (no adaptation)
```{r}
res.unc <- getUncertaintyTrajectories(E=E, slopes=slopes, orig.damage=res$orig, damage.scenario=res$scenario)
total.damage <- apply(res$yearly, 1, sum)
summary(total.damage)
```

Plot comparing distributions of total damage for various uncertainty settings
```{r}
plotFigure5b(res.unc, total.damage, ifPdf=FALSE)
```

>>>>

## Optimal timing of sea level rise adaptation measures in Bergen, Norway
### Author: Thordis L. Thorarinsdottir

@@

To run the analysis, run the main script BergenDamageData.R as shown below.

@@

Investigation of the effects of uncertainty (no adaptation).
```{r}
res.unc <- getUncertaintyTrajectories(E=E, slopes=slopes, orig.damage=res$orig, damage.scenario=res$scenario)
total.damage <- apply(res$yearly, 1, sum)
summary(total.damage)
```

Plot comparing distributions of total damage for various uncertainty settings.
```{r}
plotFigure5b(res.unc, total.damage, ifPdf=FALSE)
```
